Large language models generate code that looks uniformly confident. A correct
call to \texttt{stripe.PaymentIntent.create()} and a deprecated call to
\texttt{stripe.Charge.create()} are emitted with the same surface tone, even
when the underlying token distribution is a near-50/50 split (probability
$0.52$ vs.\ $0.47$). Code-generation uncertainty is primarily \emph{intra-generational}: visible
in the token distribution at generation time, invisible once tokens are
committed. Multi-sample methods, which detect inter-generational
inconsistency, therefore produce almost no signal on code tasks, achieving at
most $35\%$ detection on our benchmark at comparable false-positive rates,
versus $70$--$85\%$ for \eps.

We introduce \eps, a per-token normalized Shannon entropy computed from the
top-$k$ log-probabilities returned by the generation API, aggregated over the
semantic tokens of a function via AST filtering and max-pooling. \eps is
designed as a \emph{recall-maximizing filter}, not a detector. On a
30-prompt calibration benchmark across GPT-4o, GPT-4o-mini, GPT-4-turbo, and
DeepSeek V3, \eps at the \textsc{flagged} threshold ($\eps \ge 0.30$)
achieves recall $=1.00$ on true failures with precision $=0.272$ on the
evaluated 200-entry set. We compare against two alternatives at the same
$1\times$ API cost: the sequence-level mean token probability (\papg,
following Spiess et al.~\cite{spiess2025calibration}), which is competitive
on raw detection ($65$--$90\%$) but offers no token-level attribution; and
black-box multi-sample methods including UQLM, which detect $10$--$35\%$ of
version-split API failures at $5\times$ cost. A \texttt{min\_logprob}
baseline achieves $45$--$55\%$ where \eps achieves $70$--$85\%$.

The low stage-1 precision is the design. We pair the filter with a parallel
LLM review loop that reclassifies each flagged entry as \textsc{cleared} or
\textsc{confirmed}. On 201 production and scenario entries across three
models (GPT-4o, GPT-4o-mini, DeepSeek V3), a variant that injects model-specific learned false-positive
patterns into the reviewer clears $68.7\%$ of flagged entries with zero
late false positives, lifting end-to-end precision above $94\%$ (Wilson
lower bound, $n=57$). The contribution is the system: a recall-maximizing
filter verified against zero observed misses on the evaluated set, paired
with a reviewer that keeps up with machine-speed code generation, plus the
first direct three-way empirical comparison of intra-generational,
sequence-level, and inter-generational uncertainty signals on
production-realistic code prompts.
