\section{Introduction}
\label{sec:introduction}

AI-assisted developers now generate code several times faster than they can
read it. A single engineer working with a coding assistant produces pull
requests that would previously have represented days of work, and the
bottleneck shifts from writing to reviewing. Reviewers have finite
attention and cannot inspect every line with equal care, yet the failure
modes of modern code generation concentrate in small, hard-to-spot places.
Recent empirical work on deprecated APIs quantifies the scale of the
problem: LLM-based code completion emits deprecated API calls at rates of
roughly $25$--$38\%$ on standard prompts and substantially more on legacy
codebases, because the training corpus straddles library-version transitions
and the model has no posterior knowledge of deprecation at inference time~%
\cite{wang2025deprecated}. The mistakes are not exotic: they are the
ordinary traffic of a maturing ecosystem, rendered invisible by the
uniformity of LLM output.

A concrete instance. A model asked to charge a credit card might emit
\texttt{stripe.Charge.create(...)} --- deprecated since 2019 --- or
\texttt{stripe.PaymentIntent.create(...)}, the current API. Both arrive in
the developer's editor with the same syntactic fluency, the same confident
indentation, and no visible marker distinguishing a well-chosen call from
one the model guessed at. At the method-selector token, the two choices
split the probability mass near 50/50 ($0.52$ vs.\ $0.47$); the output
exposes none of this. Failures of AI code generation cluster at exactly
these points: version-split APIs, renamed SDK methods, signature changes
between library releases. The model is uncertain; the output is not.

\paragraph{Intra- versus inter-generational uncertainty.}
The gap between a $0.52$-vs-$0.47$ internal split and a confident-looking
output is not an accident of any particular model; it is structural.
Existing uncertainty-quantification methods for LLMs are overwhelmingly
\emph{inter-generational}: they sample the same prompt multiple times and
measure disagreement across completions~\cite{kuhn2023semantic,uqlm2024}.
This works when the model's uncertainty surfaces as instability across
re-rolls --- factual questions, open-ended reasoning. Code is not such a
task. A model with a $0.52$ prior on the deprecated \texttt{Charge} API
samples that branch nearly every time; once the early tokens commit, the
rest of the function is forced by context. The uncertainty exists, but it
lives \emph{inside a single generation}, in the token distribution at each
decoding step, not \emph{across} generations. We call this the
\emph{intra- versus inter-generational} distinction. It is the conceptual
foundation of this paper.

\paragraph{\eps: a recall-maximizing filter.}
We introduce \eps (epsilon), a per-token normalized Shannon entropy over
the top-$k$ log-probabilities returned during generation. After AST-based
filtering to keep only semantically meaningful tokens (attribute accesses,
keyword arguments, import targets --- not whitespace, comments, or
cosmetic identifiers), we aggregate via max-pooling to obtain a single
score per function. \eps is not a detector --- it identifies where the
model was uncertain at decoding time. At a threshold of $\eps \ge 0.30$
it catches $100\%$ of true failures on our benchmark, at the cost of
roughly $73\%$ false alarms.

\paragraph{A three-way comparison.}
The primary empirical contribution of this paper is a direct benchmark of
three fundamentally different uncertainty signals on the same
production-realistic prompts across four models. Multi-sample methods at
$N=5$, $T=0.7$ detect $10$--$35\%$ of HIGH-risk prompts at $5\times$ API
cost; the sequence-level mean token probability \papg~\cite{spiess2025calibration}
detects $65$--$90\%$ at $1\times$ cost but offers no token-level
attribution; \eps detects $70$--$85\%$ at $1\times$ cost with the specific
uncertain token localized to a line and column. \papg is competitive with
\eps on raw detection rate and in fact beats it on two of four OpenAI
models; \eps's distinguishing property is not higher detection but
\emph{where} the signal fires. The empirical case for the intra/inter
distinction now rests on direct measurement, not just the UQLM-only
comparison of earlier work.

\paragraph{The two-stage system.}
A $27\%$-precision filter is not meant to be used in isolation. Stage 2
is a parallel LLM review loop: every flagged entry is dispatched, in
parallel, to a reviewer model that returns \textsc{cleared} or
\textsc{confirmed}. At current API prices this costs fractions of a cent
per entry and completes in seconds. \eps has perfect recall but poor
precision; the reviewer has good precision but would be too expensive per
line. Filter plus reviewer gives a system with near-$100\%$ end-to-end
precision while missing nothing the filter catches. A parallel review
system scales with generation speed and moves review off the developer's
critical path.

\paragraph{Contributions.}
\begin{enumerate}[noitemsep]
    \item The intra/inter-generational distinction, formalized and with
    empirical confirmation: \eps reaches $85\%$ detection on GPT-4o
    against $10$--$35\%$ for direct multi-sample measurement and $5\%$ for
    UQLM on the same benchmark.
    \item \eps: an AST-filtered, max-aggregated token-level entropy score,
    with a three-type uncertainty taxonomy (cosmetic, consequential,
    implementation-approach) that motivates the filter design.
    \item A two-stage filter-plus-review architecture, with a context-%
    accumulation variant, evaluated on 201 entries across three models
    (GPT-4o, GPT-4o-mini, DeepSeek V3): near-$100\%$ end-to-end
    precision at $100\%$ recall. Scenario and calibration evaluation
    additionally covers GPT-4-turbo (four models total).
    \item The first direct three-way empirical comparison --- \eps vs.\
    \papg vs.\ multi-sample --- on production-realistic version-split
    prompts, isolating where each signal fires and where it does not.
\end{enumerate}

Implementation and benchmark are at
\url{https://github.com/michaeljaquith/epsilon-code}.
