\section{Related Work}
\label{sec:related}

Four adjacent lines of work inform the design of \eps: empirical studies of
deprecated API usage (which motivate the problem), token-level and
sequence-level calibration of LLMs for code (which share the underlying
logprob signal), multi-sample uncertainty quantification (which is the
dominant alternative and the closest point of comparison), and adaptive
decoding (which uses the same per-token entropy signal for a different
purpose). We review each in turn, closing with static analysis.

\subsection{Deprecated and version-split API usage}
\label{subsec:related-deprecated}

Wang et al.~\cite{wang2025deprecated} present the first systematic study of
deprecated API usage in LLM-based code completion, evaluating seven models
on 145 API mappings drawn from eight popular Python libraries across
$28{,}125$ completion prompts. They measure API Usage Plausibility (AUP)
and Deprecated Usage Rate (DUR), finding that deprecated-API emission is
prevalent across all evaluated models; the root cause they identify is
that deprecated API usages are present in training data while deprecation
status itself is not reliably propagated to inference time. Their
mitigations (REPLACEAPI and INSERTPROMPT) operate at the prompt or
post-generation level and require a known deprecation mapping.

Their finding establishes that the problem we address is common in practice
rather than a corner case: on version-split APIs and renamed SDK methods,
models routinely commit to a deprecated branch without surface indication.
Our work is complementary. Wang et al.\ measure \emph{how often} LLMs emit
deprecated code and diagnose \emph{why} the output looks confident; \eps
measures the \emph{signal at generation time} that distinguishes a
confidently-chosen branch from an internally-contested one, and routes the
latter for review. The two methods address different points in the
lifecycle: theirs a post-hoc census with library-specific mitigations,
ours a zero-overhead runtime filter that does not require an enumerated
list of deprecated symbols.

\subsection{Token-level calibration and confidence}
\label{subsec:related-calibration}

Spiess et al.~\cite{spiess2025calibration} study calibration and
correctness of language models for code, computing several confidence
signals (including the sequence-level mean token probability, which we
refer to throughout as \papg) and evaluating whether they correlate with
functional correctness on HumanEval and related benchmarks. They find
that generative code models are not well-calibrated out of the box and
that Platt scaling can recover calibration in settings where labelled
correctness data is available. The \papg signal --- the exponential of
the mean log-probability over all generated tokens --- is derived from
the same raw logprob data that \eps uses.

Four differences between that setup and ours deserve emphasis. First,
\emph{aggregation}: \papg takes a sequence-level mean of per-token
probabilities; \eps takes a max after AST filtering, so a single high-%
entropy API-selector token is not diluted by long confident stretches.
Second, \emph{filtering}: \eps restricts the input set to semantically
meaningful tokens (attribute accesses, keyword arguments, import
targets), while \papg averages over every token including whitespace and
cosmetic names. Third, \emph{prompt regime}: Spiess et al.\ evaluate on
HumanEval and similar benchmarks where correctness is well-defined by
unit tests; we evaluate on version-split API prompts where the ground
truth is ambiguous enough to require LLM judging
(\S\ref{subsec:gt-disclosure}). Fourth, \emph{use}: their work is
diagnostic (measuring calibration); ours is an active routing
mechanism. Because \papg and \eps operate on the same underlying logprobs
at the same $1\times$ API cost, a direct head-to-head comparison is
possible; we report it in \S\ref{sec:comparison}.

Earlier token-level calibration studies (Kadavath et
al.~\cite{kadavath2022language}; Varshney et al.~\cite{varshney2023stitch})
establish that LLMs are reasonably calibrated at the token level for
factual questions and that selective generation can exploit this. Our
work extends that line to code, where AST filtering is what makes per-%
token entropy actionable rather than dominated by cosmetic variance.
Conformal prediction approaches~\cite{quach2023conformal,
angelopoulos2022conformal} provide set-valued predictions with coverage
guarantees but do not localize which token within a generation is
uncertain. Uncertainty propagation through multi-stage ML pipelines is
studied in adjacent domains~\cite{jungo2020analyzing}.

\subsection{Multi-sample and behavioural-diversity methods}
\label{subsec:related-multisample}

Inter-generational methods sample the same prompt multiple times and
measure disagreement among outputs. Kuhn et al.~\cite{kuhn2023semantic}
introduce semantic entropy: multiple completions are clustered by
semantic equivalence (via natural language inference), and cross-cluster
entropy provides a hallucination signal for factual QA. UQLM~\cite{uqlm2024}
packages semantic negentropy and related signals as an open-source
library; we include it here as the closest off-the-shelf tool and report
its performance in \S\ref{sec:comparison} in one sentence. Beyond these,
a growing line of work~\cite{sharma2025multisample} applies stronger
notions of equivalence --- up to and including symbolic execution or
semantic-equivalence checks on generated code --- to improve behavioural
consistency detection specifically for code outputs.

These methods are structurally limited for the task we study.
Intra-generational uncertainty does not surface as output variation when
the distribution is peaked (as it typically is for code tokens: a
$0.52$-peaked distribution picks its peak nearly every time at temperature
$0.7$, and always at temperature $0$). A model can be internally torn
between two API calls and emit one of them unanimously across re-rolls.
The Stripe example we report empirically in
\S\ref{subsec:multisample-comp} --- GPT-4o with $\eps=0.878$ and sample
diversity $=0.00$ across $N=5$ at $T=0.7$ --- is a direct instance. A
stronger equivalence check improves precision on Type 3 (implementation-%
approach) false positives, where two semantically equivalent
implementations would be conflated by output-level diversity alone; but
it cannot recover a signal that never varies across samples in the first
place. The intra/inter distinction is not a claim that inter-generational
methods are badly implemented, only that they are measuring a different
quantity.

\subsection{Generation-time intervention and adaptive decoding}
\label{subsec:related-adadec}

AdaDec~\cite{adadec2025} reads the same per-token Shannon entropy that
\eps reads, but uses it at decoding time rather than review time: when
the entropy at the current step exceeds a learned threshold, the decoder
pauses and triggers a lookahead re-ranking step over candidate
continuations. On HumanEval and MBPP across model sizes from $0.6$B to
$8$B, AdaDec reports up to $15.5$pp improvement in Pass@1 over greedy
decoding while pausing on $3.95$--$11.88\%$ of tokens. The signal is the
same as ours; the action is different. AdaDec improves the model's own
output at generation time; \eps surfaces residual uncertainty \emph{after}
the model has committed, for routing to downstream review. The two
approaches are compatible: an AdaDec-enhanced generator still produces a
token distribution at each step, and \eps operates on whatever
distribution the final decoder emits. We do not evaluate a combined
pipeline but expect \eps values to be lower on average after AdaDec-style
intervention, with residual high-\eps tokens concentrating on
consequential decisions that even a lookahead re-rank could not resolve.

\subsection{Static analysis, linters, and execution-based evaluation}
\label{subsec:related-static}

Static analysis and linter rules catch \emph{known}-bad patterns for
specific libraries once deprecation has been encoded into a ruleset.
These approaches are complementary to \eps and represent the floor of
detection: when a rule exists, a linter will catch the problem whether
or not the model hesitated. \eps operates in the gap --- it fires where
the model itself was uncertain, which includes version splits not yet in
any ruleset (a library updated last week, a half-migrated codebase) and
internal renames that static analysis has no fact to test against.
Execution-based code-generation benchmarks~\cite{chen2021evaluating,
austin2021program,jimenez2024swebench} measure whether the output passes
test cases, not whether the model was confident; a silent dependency
update can turn a fully-passing generation into a regression that no
test in the current suite exercises. To our knowledge, no prior work
treats within-generation token-level uncertainty as a first-class
routing signal for code review; the closest is CodeT~\cite{chen2022codet}
and related self-consistency approaches, which are inter-generational by
construction, and post-generation repair with uncertainty-based
ranking~\cite{ye2022selfapr}.
