Large language models generate code that appears uniformly confident.
Developers receive no signal for which decisions warrant careful review —
yet the failure modes of code generation are not random: they cluster around
API version decisions, library selection, and architectural compatibility choices
that are systematically expensive when wrong.

Existing uncertainty quantification methods address a structurally different
problem. Multi-sample consistency methods (semantic entropy, UQLM) detect
uncertainty by sampling a prompt repeatedly and measuring variance across
outputs. For code generation, this approach fails: models have consistent
training-data priors and generate the same API choice across all samples,
regardless of whether that choice is correct. We term this the
\emph{intra- vs.\ inter-generation distinction}: code generation uncertainty
exists at generation time, in the token-level probability distribution,
and is gone from the committed output. It cannot be observed by repeated
sampling.

We introduce $\eps$ (epsilon), a token-level \emph{decision-risk prioritization
signal} that operates within a single generation using log-probabilities,
identifying where the model was uncertain at generation time, not where the
code is incorrect. We identify three
categories of token-level uncertainty in generated code --- \emph{cosmetic}
(naming), \emph{consequential} (API and library decisions), and
\emph{implementation-approach} (algorithm style) --- and show that only
consequential uncertainty correlates with real risk. We filter cosmetic
uncertainty using AST-based declaration classification, isolating the signal
that matters.

On a 30-prompt benchmark spanning three OpenAI models, simple algorithms, and
version-split API calls, $\eps$ achieves an 85\% detection rate on GPT-4o;
70\% on two additional models. UQLM, the closest published baseline,
achieves 5\% detection (1 of 20 high-uncertainty prompts) compared to 85\%
for $\eps$ --- empirically confirming that multi-sample methods are
ineffective on this problem class, consistent with a structural argument we
develop in Section~5.
The $\eps$ system adds zero latency (log-probabilities arrive with the
generation) and provides token-, line-, and function-level localization
that multi-sample methods cannot produce.
