\section{Conclusion}
\label{sec:conclusion}

LLM code generation uncertainty is intra-generational, token-level, and
decision-specific. Existing uncertainty quantification methods built for
factual hallucination detection are ineffective on this problem class by a
structural argument supported empirically --- a claim we establish
conceptually and confirm empirically with a 5\% vs.\ 85\% detection rate
comparison (GPT-4o; 70\% on two additional models) against the closest
published baseline.

The $\eps$ primitive provides a practical, zero-latency signal for developer
review prioritization. Its key properties --- single-generation measurement,
AST-filtered cosmetic exclusion, max-based aggregation, function-level
localization --- are motivated by the specific failure modes of code
generation rather than borrowed from adjacent literature.

One open question is where else the intra-generation distinction matters
beyond code generation. Others --- external validity on production
codebases, robustness to prompt variation, applicability beyond OpenAI's
logprob calibration, and user study validation --- remain open.
Code generation is not the only domain where models make consequential
decisions token-by-token with consistent cross-generation behavior. Anywhere
a model has strong training-data priors for a structured choice --- legal
clause selection, medical treatment recommendations, configuration
generation --- the same structural argument applies and the same measurement
approach may be warranted.
