\section{Discussion}
\label{sec:discussion}

\subsection{Limitations}

\paragraph{Confident wrongness.}
$\varepsilon$ cannot detect decisions the model makes confidently and incorrectly.
Scenario~B demonstrates this directly: GPT-4o generates v0 OpenAI SDK syntax
with high confidence; $\eps$ fires on surrounding function signature decisions,
not on the core API error. The system faithfully reports ``model was confident
about this choice'' --- which is true. $\eps$ is a decision-risk signal, not a
correctness oracle. Confident wrongness is an inherent limitation of any
single-generation uncertainty measure.

\paragraph{Model calibration.}
Thresholds (0.30 / 0.65 / 0.95) are calibrated to GPT-4o-2024-08-06.
Different models have different log-probability distributions and may require
recalibration. The AST filtering logic and max aggregation are model-agnostic;
only the threshold values require tuning for a new model.

\paragraph{Type~3 false positive floor.}
The 50\% false positive rate on GPT-4o (60\% on smaller models) on the LOW benchmark set is driven by
Type~3 implementation-approach uncertainty on simple utility function prompts.
In production use, code generation tools are primarily invoked for API
integration and library selection tasks --- the HIGH domain --- where Type~3
uncertainty is substantially rarer. The practical false positive rate is
expected to be lower than the benchmark figure suggests.

\paragraph{Confidently-resolved domains.}
A second category of limitation is \emph{confidently-resolved domains}:
prompts where every model has converged on a strong training-data prior,
producing $\eps_\text{file} = 0.000$ regardless of whether the confident
choice is correct. In our benchmark, current UTC datetime retrieval and
HTTP GET to JSON parsing fall into this category across all three models.
These domains are invisible to $\eps$ --- the system correctly reports that
the model was certain, but does not know whether that certainty is warranted.
For widely-deployed APIs with stable, well-documented interfaces, this is the
expected and desirable behavior. For domains where a confident model choice
is systematically wrong (e.g., a deprecated-but-confidently-recalled API),
$\eps$ provides no signal, as demonstrated by Scenario~B.

\paragraph{Adaptive threshold cold start.}
The K-NN adaptive threshold requires a warm neighborhood (5--20 similar prior
runs) before activating. New prompt types begin with absolute thresholds until
sufficient history accumulates. For Scenario~E, 13 runs were required before
the MAD domain activated --- a meaningful investment for low-volume use cases.

\subsection{Future Work}

\paragraph{Pipeline propagation.}
$\varepsilon$ is designed as an accumulating primitive: in a multi-stage
generation pipeline (e.g., plan $\to$ scaffold $\to$ implementation), each
stage's $\eps$ could be propagated forward, with cross-stage accumulation
triggering intervention at configurable thresholds. Pipeline propagation is
not yet implemented.

\paragraph{Per-token intervention.}
The current system aggregates to file and function level. Token-level
alternatives are already available in \texttt{peak\_tokens}; a future interface
could present the specific alternative tokens at the exact flagged position,
enabling targeted re-prompting rather than full re-generation.

\paragraph{Adapter for open-source models.}
Log-probabilities are available from OpenAI and Anthropic APIs and from
open-source models via vLLM or Ollama. A thin adapter layer would make the
$\eps$ system model-agnostic at the infrastructure level.
