Large language models generate code that looks uniformly confident. A
correct call to \texttt{stripe.PaymentIntent.create()} and a deprecated
call to \texttt{stripe.Charge.create()} are emitted with the same
surface tone, even when the underlying token distribution is a near-%
50/50 split ($P=0.52$ vs.\ $0.47$). Code-generation uncertainty is
primarily \emph{intra-generational}: visible in the token distribution
at generation time, invisible once tokens are committed. Sequence-level
confidence signals --- most notably the mean token probability \papg
of Spiess et al.~\cite{spiess2025calibration} --- read the same
logprobs but aggregate them into one number per function; multi-sample
methods measure output disagreement that simply does not occur for
peaked code-token distributions, detecting at most $35\%$ of HIGH-risk
prompts on our benchmark at $5\times$ cost.

We introduce \eps, a per-token normalized Shannon entropy computed from
the top-$k$ log-probabilities returned by the generation API,
AST-filtered to semantic tokens and max-pooled per function. At the
function level \eps is a recall-maximizing filter: on four models it
flags $97.1\%$ of HIGH API-integration prompts, with zero observed misses on the 200-entry evaluated set (recall-maximizing design) and
precision $=0.272$. The contribution is
not the function-level flag. The contribution is that the same score
localizes: of the $\sim 98$ tokens in a typical flagged function, only
$10.5\%$ exceed the flag threshold. \eps narrows the developer's
review surface from a whole function to an average of $10.4$ tokens
per function ($10.5\%$ of the function) --- an $89\%$ reduction in
within-function review burden. This is the distinguishing claim.
\papg, at the same $1\times$ API cost, is competitive on raw detection
($65$--$90\%$ vs.\ \eps's $70$--$85\%$ across four models) and in fact
beats \eps on two of four OpenAI models; what it cannot do is say
\emph{where in the function} to look. \eps answers both.

The low function-level precision is the design. We pair the filter
with a parallel LLM review loop that reclassifies each flagged entry
as \textsc{cleared} or \textsc{confirmed}, using \eps's token-level
attribution to direct the reviewer to the specific high-entropy
tokens that drove the score. On 201 entries across three models, a
context-primed reviewer clears $68.7\%$ of flagged entries with zero
late false positives. The contribution is the two-level view:
function-level recall plus token-level localization, together with
the first direct three-way empirical comparison of intra-generational,
sequence-level, and inter-generational uncertainty signals on
production-realistic code prompts.
